Overview of the eHealth Knowledge Discovery Challenge at IberLEF 2021

### 2021-06-18 paper/paper.tex
Sistemas

-- Describir los sistemas

>>>>

%-- Describir los sistemas
\begin{description}
  \item[uhKD4:]  system is built upon two independent deep-learning-based architectures. Accordingly, two
  different models are defined and each task is carried out separately. Task A is approached as a
  sequence labelling problem in which each token from an input sequence is assigned a label that
  represents the combination of the BILUOV entity tagging scheme with each one of the possible
  types of an entity. The BILUOV tags correspond to: Begin, to represent the start of an entity;
  Inner, to represent its continuation; Last, to represent its end; Unit, to represent single word
  entities; Other, to represent words that are not a part of any entity; and oVerlapping, to represent
  words that belong to multiple entities.Thus, the output of the model considers 21 different labels: the
  O label and the combination of the remaining tags (BILUV) and the entity types (Concept,
  Action, Predicate and Reference). The proposed approach to Task B is to solve a multi-class
  classification problem, in which given a sentence and a highlighted pair of entities, one of the
  predefined relations is assigned to occur from the first entity toward the second one. A new
  artificial relation class none is defined to symbolize the non-occurrence of any relation between
  a pair of entities.

  \item[Vicomtech Joint Classifier:] This model is the result of the revision of our participation in the previous eHealth-KD edition
  [2]. Most of the changes introduced in the current edition aim at simplifying components of
  the architecture that seemed redundant or needlessly complex. In addition, we have forgone
  the ability to predict multi-word discontinuous and/or overlapping entities like the shown in
  Figure 1, which in any case required elaborate post-processing to yield acceptable results.
  It consists of a single end-to-end deep neural network with
  pre-trained BERT models as the core for the semantic representation of the input texts, that predicts all
  the output variables—entities and relations—at the same time, modelling the whole problem jointly.
  The main change w.r.t. the original implementation affects the representation of relations. The Joint
  Classifier model achieved the first position in the main scenario of the competition and ranked second
  in the rest of the scenarios.

  \item[Vicomtech  Seq2Seq:] uses an approach based on an
  encoder-decoder model. It transduces the input text into an output sequence by reading the input text.
  The target sequence is a compact representation of the information contained in the gold-labels of
  the datasets. This approach showed a promising performance despite not being competitive enough.
  However, it poses an interesting potential future work.
  This paradigm is way more flexible because it can ingest a sequence of any length,
  and output another arbitrary sequence. That is, the output sequence is not tied to the structure
  of the input; a text-to-text model can potentially encode any sort of information

  \item[PUCRJ-PUCPR-UFMG:] a multilingual BERT-based system for joint entity recognition and relation extraction
  in multidomain texts. Our end-to-end multitasking model benefits from the transformer architecture,
  which has proved to capture better the global dependencies of the input text. Also, the use of a multilin-
  gual model contributed to our system to perform well even in the set of tests containing non-Spanish
  sentences. The method consists in an end-to-end multilingual
  BERT-based system that jointly predicts both entities and relations. During training, the
  proposed multi-task system is fine-tuned in 3 sequential steps: the first one prioritizes the entity
  recognition task whereas the second gives precedence to the relation extraction one. Finally,
  the third and last step is trained for both tasks using a multi-task strategy.

  \item[UH-MMM:]  solution solves both tasks separately and sequentially. Thus, independent models
  with different architectures and features were trained to solve the NER and RE problems. The
  main distinction between the two architectures raises from the type of problem they solve. The
  first task is posed as a tag prediction problem that takes the raw text of a sentence as input and
  outputs two independent tag sequences: one in the BILOUV tag system for entity prediction and
  another with the tags corresponding to each entity type (Concept, Action, Reference, Predicate).
  The BILOUV tag scheme classification corresponds to Begin, for the start of an entity; Inner, for
  the token in the middle; Last for the ending token; Unit, to represent single token entities; Other
  to represent tokens that do not belong to any entity, and the oVerlapping tag is used to deal
  with tokens that belong to multiple entities. On the other hand, the second task is addressed as
  a series of pairwise queries among the entities present in the target sentence, oriented towards
  identifying the relevant relations between the previously extracted entities.

  \item[(IXA):]  use the pre-trained Language Model (LM), namely XML-
  RoBERTa-base, to provide a Cross-lingual representation of tokens and the ability to transfer learning
  from general domains. system was
  designed as a pipeline of generic sequence labellers, each of them independently fine-tuned for each
  subtask. The generic sequence labeller consists of a feed-forward network that learns how to align
  a sequence of tokens into a sequence of labels regardless of the language and domain. This simple
  straightforward system ranked in the third position in the main and Entity recognition scenario and
  widely outperformed the other systems in the relation extraction scenario.

  \item[Maoqin:]  Several deep learning models are used in plain text documents, such as
  BERT-CRF, BiLSTM-CRF. Only the best result running in the local has been submitted. But the final
  result of my method is indeed very low, with a score of 0.173 (F1), ranking 9th on the leaderboard.
  Additional work needs to be done to improve our final result and complete the subtask B: relation
  extraction.

  \item[Maoquin:] For one method, the pre-trained BERT model has been taken as the basic representation.
  For another method, BiLSTM has been preferred. The system achieved unsatisfied results in the
  challenge for official evaluation in subtask A. Due to the colab’s time and resources limitation,
  some strategies were not achieved. And subtask B: Relation Extraction has not been completed.

  \item [GuanZhengyi:] . We mainly used the classic BERT+BiLSTMs+CRF model architecture and replaced BERT
  with BETO as the pre-training model. BETO is a BERT model pre-training on Spanish text. And we
  add CNN before BiLSTM for further feature extraction. Our model architecture performed well in the
  training set and development set for identifying the types of entities
  uses the pre-training model BETO with stronger text feature
  representation capabilities as the feature representation layer. After reading the eHealth 2020
  papers, we fine-tuned the above architecture. We added CNN to further extract features of
  text. We regard NER as a classification problem at the token level. We combined BETO with
  CNN, BiLSTM and CRF model to extract global and local features of the text. That means we
  input these word vectors into CNN, BiLSTM and CRF to calculate the corresponding scores and
  perform entity recognition and BIO labeling.
\end{description}
